
---
## title: "pre_class week 3"

## author: "Mingxuan Bo"
## date: "9/25/2018"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1
How many unique countries are represented per continent?

```{r}
#install.packages("dplyr")
library(dplyr)

#install.packages("gapminder")
library(gapminder)
asia<-gapminder[gapminder$continent=="Asia",]
africa<-gapminder[gapminder$continent=="Africa",]
europe<-gapminder[gapminder$continent=="Europe",]
americas<-gapminder[gapminder$continent=="Americas",]
oceania<-gapminder[gapminder$continent=="Oceania",]

length(unique(asia$country))
length(unique(africa$country))
length(unique(europe$country))
length(unique(americas$country))
length(unique(oceania$country))
```


## 2

Which European nation had the lowest GDP per capita in 1997?

```{r}
euro_1997<-gapminder[gapminder$continent=="Europe"&gapminder$year=="1997",]
euro_1997<-arrange(euro_1997,gdpPercap)
euro_1997[1,1]
```

## 3

According to the data available, what was the average life expectancy across each continent in the 1980s?

```{r}
unique(gapminder$year)
asia_1980s<-asia[asia$year=="1982"|asia$year=="1987",]
africa_1980s<-africa[africa$year=="1982"|africa$year=="1987",]
europe_1980s<-europe[europe$year=="1982"|europe$year=="1987",]
americas_1980s<-americas[americas$year=="1982"|americas$year=="1987",]
oceania_1980s<-oceania[oceania$year=="1982"|oceania$year=="1987",]

mean(asia_1980s$lifeExp)
mean(africa_1980s$lifeExp)
mean(europe_1980s$lifeExp)
mean(americas_1980s$lifeExp)
mean(oceania_1980s$lifeExp)
```

## 4

What 5 countries have the highest total GDP over all years combined?

```{r}
total_gdp_rank<-arrange(gapminder,gapminder$pop*gapminder$gdpPercap)
unique_rank<-unique(total_gdp_rank$country)
unique_rank[(length(unique_rank)-4):length(unique_rank)]
```

## 5

What countries and years had life expectancies of at least 80 years? N.b. only output the columns of interest: country, life expectancy and year (in that order).

```{r}
over_80<-gapminder[gapminder$lifeExp>=80,]
bind_cols(over_80[,1],over_80[,4],over_80[,3])
over_80$country
```

## 6

What 10 countries have the strongest correlation (in either direction) between life expectancy and per capita GDP?

```{r}
cor_countries<-summarize(group_by(gapminder,country),corr=cor(lifeExp,gdpPercap))
arrange(cor_countries,-abs(corr))[1:10,]
```


## 7

Which combinations of continent (besides Asia) and year have the highest average population across all countries?

```{r}
continent_pop<-summarize(group_by(gapminder,continent),total_pop=sum(as.numeric(pop)))
arrange(continent_pop,-total_pop)[2,]
```

## 8

Which three countries have had the most consistent population estimates (i.e. lowest standard deviation) across the years of available data?

```{r}
countries_sd<-summarize(group_by(gapminder,country),std_dev=sd(pop))
countries_sd<-arrange(countries_sd,std_dev)
countries_sd[1:3,] 
```

## 9

Subset gm to only include observations from 1992 and store the results as gm1992. What kind of object is this?

```{r}
gm1992<-filter(gapminder,year==1992)
```


## 10

Which observations indicate that the population of a country has decreased from the previous year and the life expectancy has increased from the previous year? 

```{r}
temp<-filter(gapminder,pop<lag(pop)&lifeExp>lag(lifeExp))
```
